A word-sense representation for documents based on information value and word sense disambiguation

### 2014-04-04 paper/refactor.tex
Rewrite formulas.
more text explaining results

Given $w_1, \ldots, w_M$, words of $T$ sorted by information value, and suppose that $w_{i_1}, w_{i_2}, \ldots, w_{i_n}$ are the $n$ first words  such that disambiguation for each $w_{i_j}$ is feasible. Then, the top senses for $T$ are
\begin{equation}
  WSD(w_1), WSD(w_2), \ldots, WSD(w_n)
\end{equation}

@@

\begin{equation}
  similarity(w, T) = max(path\_similarity(w, top\_senses_n(T)))
\end{equation}

@@

In Top Senses table we can observe that some senses like local\_anesthetic was matched on Whats to be done? as first result. \\
Also in State and revolution Marx was matched with a United States comedian and a similar result we got with Berstein that was matched with a composer, however in the case of Engels it was matched to a socialist who wrote the Communist Manifesto with Karl Marx. \\
$Similarities$ tables shows that, in most of the works, synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ had a lower similarity in most of the works. \\
One strange result was $Hair$ that matched second in similarity score in Imperialism, the Highest St....

>>>>

Given $w_1, \ldots, w_M$, words of $T$ sorted by information value, and suppose that $w_{i_1}, w_{i_2}, \ldots, w_{i_n}$ are the $n$ first words  such that disambiguation for each $w_{i_j}$ is feasible. Then, the top senses for $T$ are
\begin{equation}
  TS(T) = \{ WSD(w_1), WSD(w_2), \ldots, WSD(w_n) \}
\end{equation}

@@

\begin{equation}
  sim(s, T) = max \left\{ path(s,s'), s' \in TS(T) \right\}
\end{equation}

@@

First we examined the results after applying the $WSD$ algorithm (Top Senses Table). We observed that most of the senses found by our algorithm were the senses related to the works, except for some of them.\\

On "Whats to be done?" we observed that local\_anesthetic was matched as first result. \\
For "State and revolution" we noticed that Marx was matched with a United States comedian and Berstein matched with a composer from the States. However in the case of Engels, another pronoun, it was matched to a socialist who wrote the Communist Manifesto with Karl Marx. \\

We then calculated the similarities of our handpicked synsets for each work. Since our results are ordered by the similarity in general we observed that the synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ scored lower in most of the works, with some particular cases. \\

Our results shows that "Imperialism, the Highest Stage of Capitalism" have some synset that scored irregular values. This was the case for $hair$ which matched second in similarity and that $imperialism$ scored very low. The result for $imperialism$ was surprising since it is a word contained in the work title. Also $capitalism$ wasn't at top of the list for this work.\\

As for "Materialism and Empirio-Criticism" we want to point that $philosopy$ is in the top $3$.
For the synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ they scored low values in  "State and Revolution", "Materialism and Empirio-Criticism", "What Is To Be Done?" and "The Agrarian Programme of Social-Democracy in the First Russian Revolution".
